Exploiting Array Syntax in Fortran for Accelerator Programming

### 2010-12-21 opencl/papers/foropencl.tex
updates
ack!  error!

\and
\IEEEauthorblockN{Jeffrey Overbey}
\IEEEauthorblockA{Indiana University\\
overbey2@illinois.edu}

@@

The sheer complexity of programming for clusters of many or multi-core
processors with tens of millions threads of execution make the simplicity of
the data-parallel model attractive.  The increasing complexity of
todays applications (especially in light of the increasing complexity
of the hardware) and the need for portability across architectures
make a higher-level and simpler programming model like data-parallel
attractive.

>>>>

\and
\IEEEauthorblockN{Jeffrey Overbey}
\IEEEauthorblockA{University of Illinois\\at Urbana-Champaign\\
overbey2@illinois.edu}

@@

The sheer complexity of programming for clusters of many or multi-core
processors with tens of millions threads of execution makes the simplicity of
the data-parallel model attractive.  The increasing complexity of
todays applications (especially in light of the increasing complexity
of the hardware) and the need for portability across architectures
make a higher-level and simpler programming model like data-parallel
attractive.
